\LARGE \bf Learning Depth-Sensitive Conditional Random Fields for Semantic Segmentation of RGB-D Images

### 2013-09-13 paper.tex
add a star (aka dagger) to the stueckler at al result.
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4374 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

RF                      &         90.8  &   81.6        & 67.9          & 19.9          &  65.0        &  68.3 \\
RF + SP                 &         92.5  &   83.3        & 73.8          & 13.9          &  65.7        &  70.1 \\ 
RF + SP + SVM           &         94.4  &   79.1        & 64.2          & \textbf{44.0} &  70.4        &  70.3 \\
RF + SP + CRF           &         94.9  &   78.9        &          71.1 & 42.7          &\textbf{71.9} &  \textbf{72.3} \\
\cmidrule(r){1-7}
\citet{SilbermanECCV12} &         68    &   59          & 70           & 42            &  59.6        & 58.6 \\
\citet{couprie-iclr-13} &         87.3  & \textbf{86.1} & 45.3         & 35.5          &  63.5        & 64.5 \\
\citet{stueckler2013}   & \textbf{95.6} &   83.0        & \textbf{75.1}& 14.2          &  67.0        & 70.9 \\

\bottomrule
\end{tabularx}
\quad\\The best value in each column is printed in bold. The upper part of
the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
random forests prediction within superpixels, RF + SP + SVM for an SVM trained on the unary potentials, and RF + SP + CRF is
our proposed pipeline. We optimized our approach for class average
accuracy.
\end{table*}

>>>>

RF                              &         90.8  &   81.6        & 67.9          & 19.9          &  65.0        &  68.3 \\
RF + SP                         &         92.5  &   83.3        & \textbf{73.8} & 13.9          &  65.7        &  70.1 \\ 
RF + SP + SVM                   &         94.4  &   79.1        & 64.2          & \textbf{44.0} &  70.4        &  70.3 \\
RF + SP + CRF                   & \textbf{94.9} &   78.9        &          71.1 & 42.7          &\textbf{71.9} &  \textbf{72.3} \\
\cmidrule(r){1-7}
\citet{SilbermanECCV12}         &         68    &   59          & 70           & 42            &  59.6        & 58.6 \\
\citet{couprie-iclr-13}         &         87.3  & \textbf{86.1} & 45.3         & 35.5          &  63.5        & 64.5 \\
\cmidrule(r){1-7}
\citet{stueckler2013}$^\dagger$ & \textbf{95.6} &   83.0        & \textbf{75.1}& 14.2          &  67.0        & 70.9 \\

\bottomrule
\end{tabularx}
\quad\\The best value in each column is printed in bold$^\dagger$. The upper part of
the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
random forests prediction within superpixels, RF + SP + SVM for an SVM trained on the unary potentials, and RF + SP + CRF is
our proposed pipeline. We optimized our approach for class average
accuracy.\\
$^\dagger$ \footnotesize Note that the work of \citet{stueckler2013} is not directly
comparable, as they integrated information over multiple frames, and did not
measure accuracy for pixels without valid depth measurement.
\end{table*}
